Figures and results for main manuscript

### 2020-08-01 analysis/reports/manuscript_main.Rmd
k now run it all

---
title: "Synthesis report"
output: github_document
---

@@

# Datasets in S and N space

Here is where our communities fall in S and N space:

```{r datasets in s and n space}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point(alpha = .8) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_d()

```

```{r skew intervals by dataset}

ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_2t)) +
  geom_histogram() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_1t)) +
  geom_histogram() +
  facet_wrap(vars(dat), scales = "free_y")
```

>>>>

---
title: "Figures and results for main manuscript"
output: github_document
---

@@
